Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-09 Response to reviewers - r2.tex

\begin{verbatim}
On p.12, l.9-12 authors state that MUSES can be installed in every 
mobile or portable device, independently of the operating system 
and device type. This is also derived from the title "Multiplatform 
Usable Endpoint Security System".
The authors however do not provide additional details on how is this 
achieved in the practice and are there any limitations in regards to 
that. How they managed to provide the same system for Android, Windows, 
iOS, PCs, without limitations? How MUSES manage the variety of OS 
versions and underlying platform features provided to the app? This 
feature is important differentiator against some other solutions and 
in opinion of this reviewer should be elaborated in more detail.
\end{verbatim}

\textcolor{blue}{TODO - describir las limitaciones de MUSES en cada sistema}

\begin{verbatim}
When stating (p.13, l.15-24) that MUSES relies on AES based 
symmetric encryption, does it mean that information flows in 
MUSES client internally, as well as client-server communication, 
are encrypted with the same key? Does MUSES uses client specific 
and/or temporal keys? What measures are taken to protect this key 
from malicious applications both on client and server side? How 
and where is this key generated? What is lifetime of the key? In 
my opinion this part should be reworked, providing more detailed 
description of security aspects of their approach. Also please 
see security related comment bellow.
\end{verbatim}

\textcolor{blue}{We agree with the reviewer about this paragraph not being clear, which is why it has been rewritten and clarified. At the end of the introduction of Section 4 (page XX) we have improved the explanation about MUSES data security and authentication.}

\textcolor{blue}{The MUSES system also performs an authentication process when the user logs in. The MUSES server authenticates to the MUSES client by means of a self-signed certificate. The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications. When the user connects to the MUSES server for the first time, the MUSES client asks the server for the cerfiticate, wich is sent and installed in the client local database if the user credentials are right. As the user credentials are also stored in the MUSES client local database, the user can also log in to MUSES, and it therefore can apply the Device Policies. With regard to internal data security, MUSES makes use of the advantages that the OSs themselves offer to developers. More concretely, the first prototype for Android includes functionalities provided by the Android Application Sandbox \cite{blasing2010android}. This means that other applications cannot access MUSES data, nor even other developers. The only way to do this is by rooting the device, which is a state that MUSES can detect, and therefore warn about its implications. With regard to the encryption of the rest of the device data, MUSES stands for having a security policy which advices about the installation of existing open source tools \footnote{For instance, \url{https://github.com/neurodroid/cryptonite/blob/master/README.md}}, instead of having an own implementation.}

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Rewriting data security paragraph and writing response to remark ir. Closes #36

All flows of information in MUSES are encrypted using AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations of the Fact Sheet on Suite B Cryptography \cite{salter2012suite}. Also, the MUSES server authenticates to the MUSES client by means of a self-signed certificate. The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications. And finally, MUSES makes use of the fact that current OS for mobile devices provide encrypted data containers by default, like the feature used in Android Work.

@@

As results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 even before the trials period finished. Thus, we can assume that MUSES is an effective tool, even though it has the aforementioned limitation of needing an initial set of defined security rules to start working. For this, MUSES also includes a set of guidelines for the companies to build adequate security policies. For instance, the set of initially defined rules used for the trial included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.

>>>>

The MUSES system also performs an authentication process when the user logs in. The MUSES server authenticates to the MUSES client by means of a self-signed certificate. The authentication of the users is based on Spring Security, which is a Java EE framework that provides authentication, authorization and other security features for enterprise applications. When the user connects to the MUSES server for the first time, the MUSES client asks the server for the cerfiticate, wich is sent and installed in the client local database if the user credentials are right. As the user credentials are also stored in the MUSES client local database, the user can also log in to MUSES, and it therefore can apply the Device Policies. With regard to internal data security, MUSES makes use of the advantages that the OSs themselves offer to developers. More concretely, the first prototype for Android includes functionalities provided by the Android Application Sandbox \cite{blasing2010android}. This means that other applications cannot access MUSES data, nor even other developers. The only way to do this is by rooting the device, which is a state that MUSES can detect, and therefore warn about its implications. With regard to the encryption of the rest of the device data, MUSES stands for having a security policy which advices about the installation of existing open source tools \footnote{For instance, \url{https://github.com/neurodroid/cryptonite/blob/master/README.md}}, instead of having an own implementation.

@@

As results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 even before the trials period finished. Thus, we can assume that MUSES is an effective tool, even though it has the aforementioned limitation of needing an initial set of defined security rules to start working. For this, MUSES also includes a set of guidelines for the companies to build adequate security policies. For instance, the set of initially defined rules used for the trials included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.
